---
title: "Exploratory"
output: github_document
date: "2022-11-25"
---
# Preprocessing

## parts to be completed (add as your wish)

| Contents                          | Stage | Comments                |
| --------------------------------- | ----- | ----------------------- |
| separate observations             | √     |                         |
| NAs (error value)                 |       | na.omit()  other error? |
| add explanations to each variable |       |                         |
| link the address to lat&lon       |       | other ways to plot map? |
| simple scatter/box plots          |       |                         |

```{r}
library(tidyverse)
library(corrplot)
```
In the origin data, each properties are compared with three comparable rentals.
So in total, information of four building(sets) forms one observation.


```{r}
comparable_rental_income_raw = read_csv("data/DOF__Cooperative_Comparable_Rental_Income__Citywide.csv") %>%
  janitor::clean_names() %>% 
  mutate(
    building_classification = str_remove_all(building_classification, "\\s"),
    building_classification_1 = str_remove_all(building_classification_1, "\\s"),
    building_classification_2 = str_remove_all(building_classification_2, "\\s"),
    building_classification_3 = str_remove_all(building_classification_3, "\\s")
  )
head(comparable_rental_income_raw)

```

```{r}
comparable_rental_income = 
  comparable_rental_income_raw %>% 
  separate(boro_block_lot, into = c("borough", "block", "lot"), sep = "-") %>% 
  separate(boro_block_lot_1, into = c("borough_1", "block_1", "lot_1"), sep = "-") %>% 
  separate(boro_block_lot_2, into = c("borough_2", "block_2", "lot_2"), sep = "-") %>% 
  separate(boro_block_lot_3, into = c("borough_3", "block_3", "lot_3"), sep = "-") %>% 
  mutate(
    borough = case_when(
      borough == "1" ~ "Manhattan",
      borough == "2" ~ "Bronx",
      borough == "3" ~ "Brooklyn",
      borough == "4" ~ "Queens",
      borough == "5" ~ "Staten Island"),
    borough_1 = case_when(
      borough_1 == "1" ~ "Manhattan",
      borough_1 == "2" ~ "Bronx",
      borough_1 == "3" ~ "Brooklyn",
      borough_1 == "4" ~ "Queens",
      borough_1 == "5" ~ "Staten Island"),
    borough_2 = case_when(
      borough_2 == "1" ~ "Manhattan",
      borough_2 == "2" ~ "Bronx",
      borough_2 == "3" ~ "Brooklyn",
      borough_2 == "4" ~ "Queens",
      borough_2 == "5" ~ "Staten Island"),
    borough_3 = case_when(
      borough_3 == "1" ~ "Manhattan",
      borough_3 == "2" ~ "Bronx",
      borough_3 == "3" ~ "Brooklyn",
      borough_3 == "4" ~ "Queens",
      borough_3 == "5" ~ "Staten Island")
    )
  
```


### Seperate the observations:

so I would like to separate one and 3 comparables with into four subset with same variable names for further processing.

delete `distance_from_co_op_in_miles*` to make the variables consistent to each other.

```{r}
namelist = comparable_rental_income_raw %>%
  select(-c("distance_from_co_op_in_miles","distance_from_co_op_in_miles_1","distance_from_co_op_in_miles_2")) %>%
  colnames()

## to be optimized 

rentalincom_ori = comparable_rental_income_raw %>%
  select(append(namelist[1:14],"report_year"))

std_colname = colnames(rentalincom_ori)

rentalincom_c1 = comparable_rental_income_raw %>%
  select(append(namelist[15:28],"report_year"))
colnames(rentalincom_c1) = std_colname

rentalincom_c2 = comparable_rental_income_raw %>%
  select(append(namelist[29:42],"report_year"))
colnames(rentalincom_c2) = std_colname
  
rentalincom_c3 = comparable_rental_income_raw %>%
  select(append(namelist[43:56],"report_year"))
colnames(rentalincom_c3) = std_colname

transformed_rental_income = rbind(rentalincom_ori,rentalincom_c1,rentalincom_c2,rentalincom_c3)
```

### clean data 

```{r}
transformed_rental_income = transformed_rental_income %>% 
  na.omit() 

save(transformed_rental_income, file = "data/cleaned_data.RData")
```

```{r}
df = 
  transformed_rental_income %>% 
  separate(boro_block_lot, into = c("borough", "block", "lot"), sep = "-") %>% 
  mutate(
    borough = case_when(
      borough == "1" ~ "Manhattan",
      borough == "2" ~ "Bronx",
      borough == "3" ~ "Brooklyn",
      borough == "4" ~ "Queens",
      borough == "5" ~ "Staten Island")
    )
```

## plots

Overview of key variables

Which borough has the highest full_market_value?

the first rental only
```{r}
plot_borough = 
  comparable_rental_income %>% 
  drop_na() %>% 
  group_by(borough) %>% 
  summarise(mean_value = mean(full_market_value)) %>% 
  mutate(borough = fct_reorder(borough,mean_value)) %>% 
  ggplot(aes(x = borough, y = mean_value, fill = mean_value))+
  geom_bar(stat = 'identity')+
  labs(
    title = "Borough vs value",
    x = "Borough",
    y = "Mean Value"
  )+ 
  viridis::scale_color_viridis(
    name = "Classification", 
    discrete = TRUE
  )+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))+ 
  coord_flip()+
  theme_bw()

plot_borough
```

summary on all rentals
```{r}
plot_borough = 
  df %>% 
  group_by(borough) %>% 
  summarise(mean_value = mean(full_market_value),
            value_sd  = sd(full_market_value)) %>% 
  mutate(borough = fct_reorder(borough,mean_value)) %>% 
  ggplot(aes(x = borough, y = mean_value, fill = borough))+ 
  geom_bar(stat = 'identity')+
  scale_fill_manual(values=c("#D9B489", "#D49F3A", "#BC3D1C", "#4C372D", "#E8E3B9"))+
  coord_flip()+

  theme_bw()


plot_borough
```


Neighbourhoods with highest full market value(mean_value > 29000000):

```{r}
plot_neighbor = 
  comparable_rental_income_raw %>% 
  drop_na() %>% 
  group_by(neighborhood) %>% 
  summarise(mean_value = mean(full_market_value)) %>% 
  mutate(neighborhood = fct_reorder(neighborhood,mean_value)) %>% 
  filter(mean_value > 29000000) %>% 
  ggplot(aes(x = neighborhood, y = mean_value))+
  geom_point(alpha = .8, size = 0.8)+ 
  theme_bw()+ 
  labs(
    title = "Neighborhood vs value",
    x = "Neighborhood",
    y = "Mean Value"
  )+ 
  viridis::scale_color_viridis(
    name = "Classification", 
    discrete = TRUE
  )+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))

plot_neighbor
```

```{r}
plot_neighbor_1 = 
  comparable_rental_income_raw %>% 
  drop_na() %>% 
  group_by(neighborhood_1) %>% 
  summarise(mean_value_1 = mean(full_market_value_1)) %>% 
  mutate(neighborhood_1 = fct_reorder(neighborhood_1,mean_value_1)) %>% 
  filter(mean_value_1 > 29000000) %>% 
  ggplot(aes(x = neighborhood_1, y = mean_value_1))+
  geom_point(alpha = .8, size = 0.8)+ 
  theme_bw()+ 
  labs(
    title = "Neighborhood vs value",
    x = "Neighborhood",
    y = "Mean Value"
  )+ 
  viridis::scale_color_viridis(
    name = "Classification", 
    discrete = TRUE
  )+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))

plot_neighbor_1
```

```{r}
plot_neighbor_2 = 
  comparable_rental_income_raw %>% 
  drop_na() %>% 
  group_by(neighborhood_2) %>% 
  summarise(mean_value_2 = mean(full_market_value_2)) %>% 
  mutate(neighborhood_2 = fct_reorder(neighborhood_2,mean_value_2)) %>% 
  filter(mean_value_2 > 29000000) %>% 
  ggplot(aes(x = neighborhood_2, y = mean_value_2))+
  geom_point(alpha = .8, size = 0.8)+ 
  theme_bw()+ 
  labs(
    title = "Neighborhood vs value",
    x = "Neighborhood",
    y = "Mean Value"
  )+ 
  viridis::scale_color_viridis(
    name = "Classification", 
    discrete = TRUE
  )+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))

plot_neighbor_2
```

```{r}
plot_neighbor_3 = 
  comparable_rental_income_raw %>% 
  drop_na() %>% 
  group_by(neighborhood_3) %>% 
  summarise(mean_value_3 = mean(full_market_value_3)) %>% 
  mutate(neighborhood_3 = fct_reorder(neighborhood_3,mean_value_3)) %>% 
  filter(mean_value_3 > 29000000) %>% 
  ggplot(aes(x = neighborhood_3, y = mean_value_3))+
  geom_point(alpha = .8, size = 0.8)+ 
  theme_bw()+ 
  labs(
    title = "Neighborhood vs value",
    x = "Neighborhood",
    y = "Mean Value"
  )+ 
  viridis::scale_color_viridis(
    name = "Classification", 
    discrete = TRUE
  )+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))

plot_neighbor_3
```


```{r}
transformed_rental_income %>% 
  drop_na() %>% 
  ggplot(aes(x = year_built, y = full_market_value,color = building_classification))+
  geom_point(alpha = .3, size = 0.8)+ 
  theme_bw()+ 
  labs(
    title = "Total Market Value vs Year",
    x = "Year the building was built",
    y = "Total Market Value"
  )+ 
  viridis::scale_color_viridis(
    name = "Classification", 
    discrete = TRUE
  )
```

```{r}
comparable_rental_income_raw %>% 
  drop_na() %>% 
  ggplot(aes(x = year_built, y = full_market_value,color = building_classification))+
  geom_point(alpha = .8, size = 0.8)+ 
  theme_bw()+ 
  labs(
    title = "Total Market Value vs Year",
    x = "Year the building was built",
    y = "Total Market Value"
  )+ 
  viridis::scale_color_viridis(
    name = "Classification", 
    discrete = TRUE
  )
```

```{r}
comparable_rental_income_raw %>% 
  drop_na() %>% 
  ggplot(aes(x = year_built_1, y = full_market_value_1, color = building_classification_1))+
  geom_point(alpha = .8, size = 0.8)+ 
  theme_bw()+ 
  labs(
    title = "Total Market Value vs Year",
    x = "Year the building was built",
    y = "Total Market Value"
  )+ 
  viridis::scale_color_viridis(
    name = "Classification", 
    discrete = TRUE
  )
```

```{r}
comparable_rental_income_raw %>% 
  drop_na() %>% 
  ggplot(aes(x = year_built_2, y = full_market_value_2,color = building_classification_2))+
  geom_point(alpha = .8, size = 0.8)+ 
  theme_bw()+ 
  labs(
    title = "Total Market Value vs Year",
    x = "Year the building was built",
    y = "Total Market Value"
  )+ 
  viridis::scale_color_viridis(
    name = "Classification", 
    discrete = TRUE
  )
```

```{r}
comparable_rental_income_raw %>% 
  drop_na() %>% 
  ggplot(aes(x = year_built_3, y = full_market_value_3,color = building_classification_3))+
  geom_point(alpha = .8, size = 0.8)+ 
  theme_bw()+ 
  labs(
    title = "Total Market Value vs Year",
    x = "Year the building was built",
    y = "Total Market Value"
  )+ 
  viridis::scale_color_viridis(
    name = "Classification", 
    discrete = TRUE
  )
```


Correlation plots

```{r}
rentalincom_c1_1 = 
  rentalincom_c1 %>%
  drop_na()
# Plot the correlation
corr = data.frame(lapply(lapply(rentalincom_c1_1, as.factor), as.numeric))
corrplot(cor(corr), type = "lower")
```


```{r}
rentalincom_c2_1 = 
  rentalincom_c2 %>%
  drop_na()
# Plot the correlation
corr = data.frame(lapply(lapply(rentalincom_c2_1, as.factor), as.numeric))
corrplot(cor(corr), type = "lower")
```

```{r}
rentalincom_c3_1 = 
  rentalincom_c3 %>%
  drop_na()
# Plot the correlation
corr = data.frame(lapply(lapply(rentalincom_c3_1, as.factor), as.numeric))
corrplot(cor(corr), type = "lower")
```


```{r}
comparable_rental_income_raw %>% 
  
  ggplot(aes(x = estimated_gross_income, y = estimated_expense,color = building_classification))+
  geom_point(alpha = .8, size = 0.8)+ 
  theme_bw()+ 
  labs(
    title = "Expense vs Income",
    x = "Estimated Income",
    y = "Estimated Expense"
  )+ 
  viridis::scale_color_viridis(
    name = "Classification", 
    discrete = TRUE
  )

```
