---
title: "processing"
output: github_document
date: "2022-11-25"
---
# Preprocessing

## parts to be completed (add as your wish)

| Contents                          | Stage | Comments                |
| --------------------------------- | ----- | ----------------------- |
| seperate observations             | √     |                         |
| NAs (error value)                 |       | na.omit()  other error? |
| add explenations to each variable |       |                         |
| link the address to lat&lon       |       | other ways to plot map? |



```{r}
library(tidyverse)
```
In the origin data, each proporties are compared with three comparable rentals.
So in total, information of four building(sets) forms one observation.


```{r}
comparable_rental_income_raw = read_csv("data/DOF__Cooperative_Comparable_Rental_Income__Citywide.csv") %>%
  janitor::clean_names()
head(comparable_rental_income_raw)

```

### Seperate the observations:

so I would like to seperate one and 3 comparables with into four subset with same variable names for further processing.

delete `distance_from_co_op_in_miles*` to make the variables consistent to each other.

```{r}
namelist = comparable_rental_income_raw %>%
  select(-c("distance_from_co_op_in_miles","distance_from_co_op_in_miles_1","distance_from_co_op_in_miles_2")) %>%
  colnames()

## to be optimized 

rentalincom_ori = comparable_rental_income_raw %>%
  select(append(namelist[1:14],"report_year"))

std_colname = colnames(rentalincom_ori)

rentalincom_c1 = comparable_rental_income_raw %>%
  select(append(namelist[15:28],"report_year"))
colnames(rentalincom_c1) = std_colname

rentalincom_c2 = comparable_rental_income_raw %>%
  select(append(namelist[29:42],"report_year"))
colnames(rentalincom_c2) = std_colname
  
rentalincom_c3 = comparable_rental_income_raw %>%
  select(append(namelist[43:56],"report_year"))
colnames(rentalincom_c3) = std_colname

transormed_rental_income = rbind(rentalincom_ori,rentalincom_c1,rentalincom_c2,rentalincom_c3)
```

### clean data 

```{r}
transormed_rental_income = transormed_rental_income %>% 
  na.omit() 
```



