---
title: "processing"
output: github_document
date: "2022-11-25"
---
# Preprocessing

## parts to be completed (add as your wish)

| Contents                          | Stage | Comments                |
| --------------------------------- | ----- | ----------------------- |
| separate observations             | √     |                         |
| NAs (error value)                 |       | na.omit()  other error? |
| add explanations to each variable |       |                         |
| link the address to lat&lon       |       | other ways to plot map? |
| simple scatter/box plots          |       |                         |

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd('../')
path_ = getwd()
knitr::opts_knit$set(root.dir = path_) # with something else than `getwd()`
getwd()

```


```{r}
library(tidyverse)
library(corrplot)


```
In the origin data, each properties are compared with three comparable rentals.
So in total, information of four building(sets) forms one observation.


```{r}
comparable_rental_income_raw = read_csv("data/DOF__Cooperative_Comparable_Rental_Income__Citywide.csv") %>%
  janitor::clean_names()
head(comparable_rental_income_raw)

```

### Seperate the observations:

so I would like to separate one and 3 comparables with into four subset with same variable names for further processing.

delete `distance_from_co_op_in_miles*` to make the variables consistent to each other.

```{r}
namelist = comparable_rental_income_raw %>%
  select(-c("distance_from_co_op_in_miles","distance_from_co_op_in_miles_1","distance_from_co_op_in_miles_2")) %>%
  colnames()

## to be optimized 

rentalincom_ori = comparable_rental_income_raw %>%
  select(append(namelist[1:14],"report_year"))

std_colname = colnames(rentalincom_ori)

rentalincom_c1 = comparable_rental_income_raw %>%
  select(append(namelist[15:28],"report_year"))
colnames(rentalincom_c1) = std_colname

rentalincom_c2 = comparable_rental_income_raw %>%
  select(append(namelist[29:42],"report_year"))
colnames(rentalincom_c2) = std_colname
  
rentalincom_c3 = comparable_rental_income_raw %>%
  select(append(namelist[43:56],"report_year"))
colnames(rentalincom_c3) = std_colname

transformed_rental_income = rbind(rentalincom_ori,rentalincom_c1,rentalincom_c2,rentalincom_c3)
```

### clean data 

```{r}
transformed_rental_income = transformed_rental_income %>% 
  na.omit() 
```

### add zoning info for the dataset
Because our data only include `boro_block_lot`, which is the tax identification of a building, if we need to mark the building on the map, we need to map the zoning of the building on the map.
```{r}
find_zoning = function(block_id){
  taxlot_to_zoning[taxlot_to_zoning$tax_block==block_id,] %>%
  head(1) %>%
  pull(zoning_district_1)
}
transformed_rental_income =
  transformed_rental_income %>%
  mutate(
    block_id = as.numeric(substr(boro_block_lot,3,7)),
    boro_block = as.numeric(paste0(substr(boro_block_lot,1,1),substr(boro_block_lot,3,7)))
  ) 

taxlot_to_zoning = read_csv("data/taxlot_to_zoning.csv") %>%
  janitor::clean_names() %>%
  filter(tax_block %in% transformed_rental_income$block_id) %>%
  distinct(tax_block,zoning_district_1)

transformed_rental_income =
transformed_rental_income %>%
  filter(block_id %in% taxlot_to_zoning$tax_block) %>%
  mutate(
    zoning = map_chr(block_id,find_zoning)
  )
    
save(transformed_rental_income, file = "data/cleaned_data.RData")
# because shiny can only access its own directory....
save(transformed_rental_income, file = "Shiny_Map/cleaned_data.RData")
```


### Data description

Boro-Block-Lot: Borough-Block-Lot(BBL) location

```{r}
comparable_rental_income_raw %>% distinct(building_classification)
comparable_rental_income_raw %>% distinct(neighborhood)
comparable_rental_income_raw %>% distinct(year_built)
```

Gross SqFt: Gross square footage of the building
Estimated Gross Income: Estimated Income per SquareFoot * Gross SquareFoot
Gross Income per SqFt: Estimated income per squarefoot of median comparable
Estimated Expense: Estimated Expense per SquareFoot * Gross SquareFoot
Expense per SqFt: Estimated expense per squarefoot of median comparab
Net Operating Income: Estimated Gross Income-Estimated Expense
Full Market Value: Current year’s total market value of the land and building
Market Value per SqFt: Full Market Value/ Gross SquareFoot
Distance from Co-op in miles: calculated distance from comparable to the subject

## plots
#built year vs value
```{r}
comparable_rental_income_raw %>% 
  
  ggplot(aes(x = year_built, y = full_market_value,color = building_classification))+
  geom_point(alpha = .8, size = 0.8)+ 
  theme_bw()+ 
  labs(
    title = "Total Market Value vs Year",
    x = "Year the building was built",
    y = "Total Market Value"
  )+ 
  viridis::scale_color_viridis(
    name = "Classification", 
    discrete = TRUE
  )
```


```{r}
plot_neighbor = 
  comparable_rental_income_raw %>% 
  drop_na() %>% 
  group_by(neighborhood) %>% 
  summarise(mean_value = mean(full_market_value)) %>% 
  mutate(neighborhood = fct_reorder(neighborhood,mean_value)) %>% 
  filter(mean_value > 29000000) %>% 
  ggplot(aes(x = neighborhood, y = mean_value))+
  geom_point(alpha = .8, size = 0.8)+ 
  theme_bw()+ 
  labs(
    title = "Neighborhood vs value",
    x = "Neighborhood",
    y = "Mean Value"
  )+ 
  viridis::scale_color_viridis(
    name = "Classification", 
    discrete = TRUE
  )+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 1))

plot_neighbor
```


```{r}
comparable_rental_income_raw %>% 
  
  ggplot(aes(x = estimated_gross_income, y = estimated_expense,color = building_classification))+
  geom_point(alpha = .8, size = 0.8)+ 
  theme_bw()+ 
  labs(
    title = "Expense vs Income",
    x = "Estimated Income",
    y = "Estimated Expense"
  )+ 
  viridis::scale_color_viridis(
    name = "Classification", 
    discrete = TRUE
  )

```
correlation
```{r}
rentalincom_c1_1 = 
  rentalincom_c1 %>%
  drop_na()
# Plot the correlation
corr = data.frame(lapply(lapply(rentalincom_c1_1, as.factor), as.numeric))
corrplot(cor(corr), type = "lower")
```

```{r}
rentalincom_c2_1 = 
  rentalincom_c2 %>%
  drop_na()
# Plot the correlation
corr = data.frame(lapply(lapply(rentalincom_c2_1, as.factor), as.numeric))
corrplot(cor(corr), type = "lower")
```

```{r}
rentalincom_c3_1 = 
  rentalincom_c3 %>%
  drop_na()
# Plot the correlation
corr = data.frame(lapply(lapply(rentalincom_c3_1, as.factor), as.numeric))
corrplot(cor(corr), type = "lower")
```
```





