---
title: "processing"
output: github_document
date: "2022-11-25"
---
# Preprocessing

## parts to be completed (add as your wish)

| Contents                          | Stage | Comments                |
| --------------------------------- | ----- | ----------------------- |
| separate observations             | √     |                         |
| NAs (error value)                 |       | na.omit()  other error? |
| add explanations to each variable |       |                         |
| link the address to lat&lon       |       | other ways to plot map? |
| simple scatter/box plots          |       |                         |

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd('../')
path_ = getwd()
knitr::opts_knit$set(root.dir = path_) # with something else than `getwd()`
getwd()

```


```{r}
library(tidyverse)
library(corrplot)
library(sf)

```
In the origin data, each properties are compared with three comparable rentals.
So in total, information of four building(sets) forms one observation.


```{r}
comparable_rental_income_raw = read_csv("data/DOF__Cooperative_Comparable_Rental_Income__Citywide.csv") %>%
  janitor::clean_names()
head(comparable_rental_income_raw)

```

### Seperate the observations:

so I would like to separate one and 3 comparables with into four subset with same variable names for further processing.

delete `distance_from_co_op_in_miles*` to make the variables consistent to each other.

```{r}
namelist = comparable_rental_income_raw %>%
  select(-c("distance_from_co_op_in_miles","distance_from_co_op_in_miles_1","distance_from_co_op_in_miles_2")) %>%
  colnames()

## to be optimized 

rentalincom_ori = comparable_rental_income_raw %>%
  select(append(namelist[1:14],"report_year"))

std_colname = colnames(rentalincom_ori)

rentalincom_c1 = comparable_rental_income_raw %>%
  select(append(namelist[15:28],"report_year"))
colnames(rentalincom_c1) = std_colname

rentalincom_c2 = comparable_rental_income_raw %>%
  select(append(namelist[29:42],"report_year"))
colnames(rentalincom_c2) = std_colname
  
rentalincom_c3 = comparable_rental_income_raw %>%
  select(append(namelist[43:56],"report_year"))
colnames(rentalincom_c3) = std_colname

transformed_rental_income = rbind(rentalincom_ori,rentalincom_c1,rentalincom_c2,rentalincom_c3)
```

### clean data 

```{r}
transformed_rental_income = transformed_rental_income %>% 
  na.omit() 
```

### add zoning info for the dataset
Because our data only include `boro_block_lot`, which is the tax identification of a building, if we need to mark the building on the map, we need to map the zoning of the building on the map.
```{r}
taxlot_to_zoning = read_csv("data/taxlot_to_zoning.csv") %>%
  janitor::clean_names() %>%
  mutate(
    boro_block = as.numeric(borough_code * 100000 + tax_block)
  ) %>%
  select(boro_block,zoning_district_1) %>%
  distinct(boro_block, .keep_all = TRUE)

expanded_df = 
  tibble(boro_block = 1:600000) %>%
  full_join(taxlot_to_zoning,by = "boro_block")

transformed_rental_income =
  transformed_rental_income %>%
  mutate(
    block_id = as.numeric(substr(boro_block_lot,3,7)),
    boro_block = as.numeric(paste0(substr(boro_block_lot,1,1),substr(boro_block_lot,3,7))),
    zoning = expanded_df$zoning_district_1[boro_block]
  )
  
```


### Data description

Boro-Block-Lot: Borough-Block-Lot(BBL) location

```{r}
comparable_rental_income_raw %>% distinct(building_classification)
comparable_rental_income_raw %>% distinct(neighborhood)
comparable_rental_income_raw %>% distinct(year_built)
```

Gross SqFt: Gross square footage of the building
Estimated Gross Income: Estimated Income per SquareFoot * Gross SquareFoot
Gross Income per SqFt: Estimated income per squarefoot of median comparable
Estimated Expense: Estimated Expense per SquareFoot * Gross SquareFoot
Expense per SqFt: Estimated expense per squarefoot of median comparab
Net Operating Income: Estimated Gross Income-Estimated Expense
Full Market Value: Current year’s total market value of the land and building
Market Value per SqFt: Full Market Value/ Gross SquareFoot
Distance from Co-op in miles: calculated distance from comparable to the subject

### Somehow, we need the location of each block.
Without copying file from `Shiny_Map`, directly use it...
```{r}
ave_location = function(geom,id){
  mean(geom[[1]][[1]][,id])
}

block_edge = read_sf("Shiny_Map/DTM_Tax_Block_Polygon.shp") %>%
  st_transform("NAD83") %>%
  mutate(
    ave_long = map_dbl(geometry,~ave_location(.x,1)),
    ave_lat = map_dbl(geometry,~ave_location(.x,2)),
    boro_block = as.numeric(BORO) * 100000 + as.numeric(BLOCK)
  ) %>%
  as_tibble() %>%
  select(boro_block,ave_long,ave_lat) %>%
  arrange(boro_block) %>%
  na.omit() %>%
  group_by(boro_block) %>%
  summarise(
    long = mean(ave_long),
    lat = mean(ave_lat)
  )
  
expanded_df = 
  tibble(boro_block = 1:600000) %>%
  full_join(block_edge)

transformed_rental_income =
  transformed_rental_income %>%
  mutate(
    longitude = expanded_df$long[boro_block],
    latitude = expanded_df$lat[boro_block]
  ) %>%
  select(boro_block_lot,boro_block,block_id,longitude,latitude,zoning,everything())


save(transformed_rental_income, file = "data/cleaned_data.RData")
# because shiny can only access its own directory....
save(transformed_rental_income, file = "Shiny_Map/cleaned_data.RData")

```


